---
title: "ReadMe"
author: "David Matsumura"
date: "September 27, 2015"
output: html_document
---

#Baseball Team Chooser Application

##Summary
This is an application built to help a person pick a baseball team.  It takes 3 inputs from the user: League, the minimun number of wins and if the team is playoff bound.

Then it filters the full team list based on that criteria and picks randomly from the remaining group.  It returns the logo of the team that it lands on.

##Summary of Program

###UI.R

```{r eval=FALSE}
library(shiny)

shinyUI(pageWithSidebar(
  headerPanel("For Whom Should I Cheer?"),
  sidebarPanel(
    selectInput("league", "Which League?", 
                choices = c("National",
                           "American")),
    sliderInput('wins',"Minimun Number of Wins",min=1,max=100,value=50),
    radioButtons("playoffs", "Headed for the Playoffs?",
                 choices = c('Yes','Does not Matter'), selected = NULL, inline = FALSE)
    ),
  mainPanel(
    imageOutput('image')
  )
))
```

It is a very simple app.  It creates the header (headerPanel). There are 3 inputs in the sidebar panel, one select input (dropdown) one slider input and one radio button.  Then it creates a spot for the output.

###Server.R


```{r, eval=FALSE}
library(shiny)

wd.datapath = paste0(getwd(),"/data")
wd.init = getwd()
setwd(wd.datapath)

teamlistinitial <- read.csv('standings.csv',stringsAsFactors=FALSE)

setwd(wd.init)
```

The server code first has to build the team datalist out of a server side CSV file.

```{r eval=FALSE}
shinyServer(function(input, output) {
  data <- reactive({ 
    LG <- switch(input$league,
                  "National" = 'NL',
                  "American" = 'AL')
    PLAY <- switch(input$playoffs,
                 "Yes" = 10,
                 "No" = 32)
    teamlist <- teamlistinitial
    teamlist <- subset(teamlist,teamlist$Lg==LG)
    teamlist <- subset(teamlist,teamlist$W > input$wins)
    teamlist <- subset(teamlist,Rk < PLAY)
    team <- teamlist$Tm[sample(1:length(teamlist$Tm),1)]
  })=
```

To actually evaluate the inputs, the server function first translates them into values that can be applied to the source dataset.  Then it applies the filters and subsets the team list.

```{r eval=FALSE}
  output$team_image <- renderImage({
    src_link <- paste('images/',team(),'.jpg',sep='')
    alt_txt <- team()
    return(list(
        src = src_link,
        contentType = "image/jpg",
        alt = alt_txt
      ))
    }, deleteFile = FALSE)
  
})
```

After the team is picked, the server calls up the matching logo from the image folder and pushes it to the output.

One useful tip: The ouput of the reactive function is a closure. It is not subsettable, nor is it coerceable to a character.  The best way to use it is to call it as is with '()' after.  (See team() being called to get the image.)